Towards Efficient First-Order Model Counting

### 2024-04-11 doc/plot.tex
Restructure the paper (and other changes)

% Created by tikzDevice version 0.12.6 on 2024-04-01 09:58:28
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (240.29,135.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 54.53) --
	( 37.95, 54.50) --
	( 41.06, 54.50) --
	( 44.17, 54.49) --
	( 47.29, 54.49) --
	( 50.40, 54.49) --
	( 53.51, 54.49) --
	( 56.62, 54.50) --
	( 59.73, 54.50) --
	( 62.85, 54.49) --
	( 65.96, 54.49) --
	( 69.07, 54.49) --
	( 72.18, 54.49) --
	( 75.30, 54.49) --
	( 78.41, 54.50) --
	( 81.52, 54.50) --
	( 84.63, 54.50) --
	( 87.74, 54.50) --
	( 90.86, 54.49) --
	( 93.97, 54.50) --
	( 97.08, 54.50) --
	(100.19, 54.49) --
	(103.31, 54.50) --
	(106.42, 54.50) --
	(109.53, 54.50) --
	(112.64, 54.50) --
	(115.75, 54.49) --
	(118.87, 54.50) --
	(121.98, 54.50) --
	(125.09, 54.50) --
	(128.20, 54.50) --
	(131.32, 54.50) --
	(134.43, 54.50) --
	(137.54, 54.50) --
	(140.65, 54.50);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 52.07) --
	( 37.95, 52.04) --
	( 41.06, 52.04) --
	( 44.17, 52.04) --
	( 47.29, 52.04) --
	( 50.40, 52.05) --
	( 53.51, 52.04) --
	( 56.62, 52.05) --
	( 59.73, 52.04) --
	( 62.85, 52.04) --
	( 65.96, 52.04) --
	( 69.07, 52.04) --
	( 72.18, 52.04) --
	( 75.30, 52.04) --
	( 78.41, 52.05) --
	( 81.52, 52.05) --
	( 84.63, 52.04) --
	( 87.74, 52.04) --
	( 90.86, 52.09) --
	( 93.97, 52.05) --
	( 97.08, 52.05) --
	(100.19, 52.05) --
	(103.31, 52.05) --
	(106.42, 52.04) --
	(109.53, 52.04) --
	(112.64, 52.04) --
	(115.75, 52.04) --
	(118.87, 52.04) --
	(121.98, 52.04) --
	(125.09, 52.05) --
	(128.20, 52.05) --
	(131.32, 52.05) --
	(134.43, 52.04) --
	(137.54, 52.05) --
	(140.65, 52.04);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 49.39) --
	( 37.95, 49.33) --
	( 41.06, 49.33) --
	( 44.17, 49.33) --
	( 47.29, 49.33) --
	( 50.40, 49.33) --
	( 53.51, 49.33) --
	( 56.62, 49.35) --
	( 59.73, 49.35) --
	( 62.85, 49.33) --
	( 65.96, 49.33) --
	( 69.07, 49.33) --
	( 72.18, 49.33) --
	( 75.30, 49.33) --
	( 78.41, 49.33) --
	( 81.52, 49.35) --
	( 84.63, 49.35) --
	( 87.74, 49.35) --
	( 90.86, 49.33) --
	( 93.97, 49.33) --
	( 97.08, 49.33) --
	(100.19, 49.33) --
	(103.31, 49.33) --
	(106.42, 49.33) --
	(109.53, 49.35) --
	(112.64, 49.35) --
	(115.75, 49.33) --
	(118.87, 49.33) --
	(121.98, 49.33) --
	(125.09, 49.33) --
	(128.20, 49.33) --
	(131.32, 49.33) --
	(134.43, 49.35) --
	(137.54, 49.35) --
	(140.65, 49.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 30.63) --
	( 37.95, 30.63) --
	( 41.06, 31.33) --
	( 44.17, 31.33) --
	( 47.29, 32.63) --
	( 50.40, 33.82) --
	( 53.51, 35.96) --
	( 56.62, 37.83) --
	( 59.73, 40.62) --
	( 62.85, 43.28) --
	( 65.96, 46.30) --
	( 69.07, 50.22) --
	( 72.18, 53.16) --
	( 75.30, 57.14) --
	( 78.41, 60.47) --
	( 81.52, 64.05) --
	( 84.63, 72.20) --
	( 87.74, 71.34) --
	( 90.86, 80.12) --
	( 93.97, 80.67) --
	( 97.08, 83.21) --
	(100.19, 89.74) --
	(103.31, 87.61) --
	(106.42, 96.04) --
	(109.53, 98.47) --
	(112.64, 99.99) --
	(115.75,103.72) --
	(118.87,103.27) --
	(121.98,109.92) --
	(125.09,111.85) --
	(128.20,115.67) --
	(131.32,116.78) --
	(134.43,119.28) --
	(137.54,123.20) --
	(140.65,125.87);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 29.90) --
	( 37.95, 30.63) --
	( 41.06, 30.63) --
	( 44.17, 29.90) --
	( 47.29, 30.63) --
	( 50.40, 31.33) --
	( 53.51, 32.63) --
	( 56.62, 33.82) --
	( 59.73, 35.45) --
	( 62.85, 38.26) --
	( 65.96, 40.62) --
	( 69.07, 42.34) --
	( 72.18, 46.05) --
	( 75.30, 49.23) --
	( 78.41, 52.36) --
	( 81.52, 64.35) --
	( 84.63, 58.30) --
	( 87.74, 68.19) --
	( 90.86, 70.67) --
	( 93.97, 72.59) --
	( 97.08, 78.45) --
	(100.19, 78.57) --
	(103.31, 83.81) --
	(106.42, 86.56) --
	(109.53, 85.94) --
	(112.64, 92.57) --
	(115.75, 95.46) --
	(118.87, 98.41) --
	(121.98,102.64) --
	(125.09,102.38) --
	(128.20,106.28) --
	(131.32,110.72) --
	(134.43,112.06) --
	(137.54,116.16) --
	(140.65,119.03);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 34.38) --
	( 37.95, 34.38) --
	( 41.06, 34.93) --
	( 44.17, 35.45) --
	( 47.29, 34.93) --
	( 50.40, 34.93) --
	( 53.51, 34.93) --
	( 56.62, 34.93) --
	( 59.73, 34.93) --
	( 62.85, 36.92) --
	( 65.96, 35.45) --
	( 69.07, 34.93) --
	( 72.18, 35.96) --
	( 75.30, 35.45) --
	( 78.41, 35.45) --
	( 81.52, 34.93) --
	( 84.63, 34.93) --
	( 87.74, 34.93) --
	( 90.86, 35.45) --
	( 93.97, 35.45) --
	( 97.08, 34.93) --
	(100.19, 34.93) --
	(103.31, 35.45) --
	(106.42, 34.93) --
	(109.53, 36.92) --
	(112.64, 34.93) --
	(115.75, 35.45) --
	(118.87, 35.45) --
	(121.98, 34.93) --
	(125.09, 34.93) --
	(128.20, 34.93) --
	(131.32, 34.93) --
	(134.43, 34.93) --
	(137.54, 35.45) --
	(140.65, 34.93);
\definecolor{drawColor}{gray}{0.70}

@@

\path[fill=fillColor] (154.94, 96.84) rectangle (212.73,147.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {bijections};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {functions};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

>>>>

% Created by tikzDevice version 0.12.6 on 2024-04-04 08:49:14
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (240.29,135.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 52.07) --
	( 37.95, 52.04) --
	( 41.06, 52.04) --
	( 44.17, 52.04) --
	( 47.29, 52.04) --
	( 50.40, 52.05) --
	( 53.51, 52.04) --
	( 56.62, 52.05) --
	( 59.73, 52.04) --
	( 62.85, 52.04) --
	( 65.96, 52.04) --
	( 69.07, 52.04) --
	( 72.18, 52.04) --
	( 75.30, 52.04) --
	( 78.41, 52.05) --
	( 81.52, 52.05) --
	( 84.63, 52.04) --
	( 87.74, 52.04) --
	( 90.86, 52.09) --
	( 93.97, 52.05) --
	( 97.08, 52.05) --
	(100.19, 52.05) --
	(103.31, 52.05) --
	(106.42, 52.04) --
	(109.53, 52.04) --
	(112.64, 52.04) --
	(115.75, 52.04) --
	(118.87, 52.04) --
	(121.98, 52.04) --
	(125.09, 52.05) --
	(128.20, 52.05) --
	(131.32, 52.05) --
	(134.43, 52.04) --
	(137.54, 52.05) --
	(140.65, 52.04);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 54.53) --
	( 37.95, 54.50) --
	( 41.06, 54.50) --
	( 44.17, 54.49) --
	( 47.29, 54.49) --
	( 50.40, 54.49) --
	( 53.51, 54.49) --
	( 56.62, 54.50) --
	( 59.73, 54.50) --
	( 62.85, 54.49) --
	( 65.96, 54.49) --
	( 69.07, 54.49) --
	( 72.18, 54.49) --
	( 75.30, 54.49) --
	( 78.41, 54.50) --
	( 81.52, 54.50) --
	( 84.63, 54.50) --
	( 87.74, 54.50) --
	( 90.86, 54.49) --
	( 93.97, 54.50) --
	( 97.08, 54.50) --
	(100.19, 54.49) --
	(103.31, 54.50) --
	(106.42, 54.50) --
	(109.53, 54.50) --
	(112.64, 54.50) --
	(115.75, 54.49) --
	(118.87, 54.50) --
	(121.98, 54.50) --
	(125.09, 54.50) --
	(128.20, 54.50) --
	(131.32, 54.50) --
	(134.43, 54.50) --
	(137.54, 54.50) --
	(140.65, 54.50);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 49.39) --
	( 37.95, 49.33) --
	( 41.06, 49.33) --
	( 44.17, 49.33) --
	( 47.29, 49.33) --
	( 50.40, 49.33) --
	( 53.51, 49.33) --
	( 56.62, 49.35) --
	( 59.73, 49.35) --
	( 62.85, 49.33) --
	( 65.96, 49.33) --
	( 69.07, 49.33) --
	( 72.18, 49.33) --
	( 75.30, 49.33) --
	( 78.41, 49.33) --
	( 81.52, 49.35) --
	( 84.63, 49.35) --
	( 87.74, 49.35) --
	( 90.86, 49.33) --
	( 93.97, 49.33) --
	( 97.08, 49.33) --
	(100.19, 49.33) --
	(103.31, 49.33) --
	(106.42, 49.33) --
	(109.53, 49.35) --
	(112.64, 49.35) --
	(115.75, 49.33) --
	(118.87, 49.33) --
	(121.98, 49.33) --
	(125.09, 49.33) --
	(128.20, 49.33) --
	(131.32, 49.33) --
	(134.43, 49.35) --
	(137.54, 49.35) --
	(140.65, 49.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 29.90) --
	( 37.95, 30.63) --
	( 41.06, 30.63) --
	( 44.17, 29.90) --
	( 47.29, 30.63) --
	( 50.40, 31.33) --
	( 53.51, 32.63) --
	( 56.62, 33.82) --
	( 59.73, 35.45) --
	( 62.85, 38.26) --
	( 65.96, 40.62) --
	( 69.07, 42.34) --
	( 72.18, 46.05) --
	( 75.30, 49.23) --
	( 78.41, 52.36) --
	( 81.52, 64.35) --
	( 84.63, 58.30) --
	( 87.74, 68.19) --
	( 90.86, 70.67) --
	( 93.97, 72.59) --
	( 97.08, 78.45) --
	(100.19, 78.57) --
	(103.31, 83.81) --
	(106.42, 86.56) --
	(109.53, 85.94) --
	(112.64, 92.57) --
	(115.75, 95.46) --
	(118.87, 98.41) --
	(121.98,102.64) --
	(125.09,102.38) --
	(128.20,106.28) --
	(131.32,110.72) --
	(134.43,112.06) --
	(137.54,116.16) --
	(140.65,119.03);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 30.63) --
	( 37.95, 30.63) --
	( 41.06, 31.33) --
	( 44.17, 31.33) --
	( 47.29, 32.63) --
	( 50.40, 33.82) --
	( 53.51, 35.96) --
	( 56.62, 37.83) --
	( 59.73, 40.62) --
	( 62.85, 43.28) --
	( 65.96, 46.30) --
	( 69.07, 50.22) --
	( 72.18, 53.16) --
	( 75.30, 57.14) --
	( 78.41, 60.47) --
	( 81.52, 64.05) --
	( 84.63, 72.20) --
	( 87.74, 71.34) --
	( 90.86, 80.12) --
	( 93.97, 80.67) --
	( 97.08, 83.21) --
	(100.19, 89.74) --
	(103.31, 87.61) --
	(106.42, 96.04) --
	(109.53, 98.47) --
	(112.64, 99.99) --
	(115.75,103.72) --
	(118.87,103.27) --
	(121.98,109.92) --
	(125.09,111.85) --
	(128.20,115.67) --
	(131.32,116.78) --
	(134.43,119.28) --
	(137.54,123.20) --
	(140.65,125.87);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 34.38) --
	( 37.95, 34.38) --
	( 41.06, 34.93) --
	( 44.17, 35.45) --
	( 47.29, 34.93) --
	( 50.40, 34.93) --
	( 53.51, 34.93) --
	( 56.62, 34.93) --
	( 59.73, 34.93) --
	( 62.85, 36.92) --
	( 65.96, 35.45) --
	( 69.07, 34.93) --
	( 72.18, 35.96) --
	( 75.30, 35.45) --
	( 78.41, 35.45) --
	( 81.52, 34.93) --
	( 84.63, 34.93) --
	( 87.74, 34.93) --
	( 90.86, 35.45) --
	( 93.97, 35.45) --
	( 97.08, 34.93) --
	(100.19, 34.93) --
	(103.31, 35.45) --
	(106.42, 34.93) --
	(109.53, 36.92) --
	(112.64, 34.93) --
	(115.75, 35.45) --
	(118.87, 35.45) --
	(121.98, 34.93) --
	(125.09, 34.93) --
	(128.20, 34.93) --
	(131.32, 34.93) --
	(134.43, 34.93) --
	(137.54, 35.45) --
	(140.65, 34.93);
\definecolor{drawColor}{gray}{0.70}

@@

\path[fill=fillColor] (154.94, 96.84) rectangle (224.55,147.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {functions};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {permutations};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}
